Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-29 paper/main.tex
rewrite figure caption

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.24\textwidth]
        {docs/source/_static/fitting-methods/progressions-1.pdf}
        \node at (0.025, 0.975)[anchor=north west, white]{\textbf{A}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.24\textwidth]
        {docs/source/_static/fitting-methods/progressions-2.pdf}
        \node at (0.025, 0.975)[anchor=north west, white]{\textbf{B}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.24\textwidth]
        {docs/source/_static/fitting-methods/progressions-3.pdf}
        \node at (0.025, 0.975)[anchor=north west, white]{\textbf{C}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.24\textwidth]
        {docs/source/_static/fitting-methods/progressions-4.pdf}
        \node at (0.025, 0.975)[anchor=north west, white]{\textbf{D}};
    \end{tikzonimage}\\
    \begin{minipage}{\textwidth}
        \begin{tikzonimage}[width=0.48\textwidth]
            {docs/source/_static/fitting-methods/extract_positionsdivision-comparison.pdf}
            \node at (0, 1)[anchor=north west]{\textbf{E}};
        \end{tikzonimage}%
        \hspace{0.01\textwidth}%
        \begin{tikzonimage}[width=0.48\textwidth]
            {docs/source/_static/fitting-methods/penalty-time-flow.pdf}
            \node at (0, 0.975)[anchor=north west]{\textbf{F}};
        \end{tikzonimage}%
    \end{minipage}
    \caption{
        The figure shows two masks (A,B) which will be compared against each other.
        Image (B) contains more cells which are a result of cellular division events that have not
        yet occurred in image (A).
        (C) "Naive" comparison of cell masks, which identifies pixels of non-matching colors and
        assigns a cost by counting these pixels.
        This simple approach does not take into consideration the parental relationship.
        This approach is displayed in (D) where pixels of cells that are directly related have been
        colored in gray.
        (E) A schematic representation of the comparison problem involving multiple cells at
        different generations.
        An initial configuration produces two results by utilizing distinct methods (i.e. evoling
        our computational model in time or assigning the data for next time point).
        (F) Comparison of cost functions, exponential regression (ER) and number of cells.
        % Total cost between successive iteration steps $t_n,t_{n+1}$.
        The overall shape of the cost is expected to have the slope of an exponential function.
        We can clearly see that division events introduce jumps within this relationship.
        In the case where we account for the parental relationship, these jumps are mitigated.
        The cost value was set to $0$ for pixel-comparisons which belong to cells that are in a
        parental relationship.
    }
    \label{fig:mask-difference-metric}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.24\textwidth]
        {docs/source/_static/fitting-methods/progressions-1.pdf}
        \node at (0.025, 0.975)[anchor=north west, white]{\textbf{A}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.24\textwidth]
        {docs/source/_static/fitting-methods/progressions-2.pdf}
        \node at (0.025, 0.975)[anchor=north west, white]{\textbf{B}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.24\textwidth]
        {docs/source/_static/fitting-methods/progressions-3.pdf}
        \node at (0.025, 0.975)[anchor=north west, white]{\textbf{C}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.24\textwidth]
        {docs/source/_static/fitting-methods/progressions-4.pdf}
        \node at (0.025, 0.975)[anchor=north west, white]{\textbf{D}};
    \end{tikzonimage}\\
    \begin{minipage}{\textwidth}
        \begin{tikzonimage}[width=0.48\textwidth]
            {docs/source/_static/fitting-methods/extract_positionsdivision-comparison.pdf}
            \node at (0, 1)[anchor=north west]{\textbf{E}};
        \end{tikzonimage}%
        \hspace{0.01\textwidth}%
        \begin{tikzonimage}[width=0.48\textwidth]
            {docs/source/_static/fitting-methods/penalty-time-flow.pdf}
            \node at (0, 0.975)[anchor=north west]{\textbf{F}};
        \end{tikzonimage}%
    \end{minipage}
    \caption{
        (A,B) Sequential simulatin masks before and after division event.
        (C) Naive pixel-wise comparison, not accounting for parental relationships.
        White regions indicate mismatches, black indicates matches.
        (D) Lineage-aware comparison. Parental relationships have been marked in gray, resulting in
        a modified penalty.
        (E) Schematic of topological difference between model and data due to division.
        (F) Evolution of cost functions applied to successive time steps $t_n$ and $t_{n+1}$,
        exponential regression (ER) and total number of cells.
        The naive metric (solid line) spikes at division events while the lineage-aware metric
        (dashed line) eliminates discontinuities, following the expected exponential scaling (ER).
        The exponential regression is fitted to the lineage-aware data.
    }
    \label{fig:mask-difference-metric}
\end{figure}
